---
title: "20BCE1025_Abhishek_N_N_Exp-7 Statistical Analysis of quantitative data"
author: "20BCE1025_Abhishek_N_N"
date: "2022-10-03"
output: pdf_document
---
Use the newsurvey data obtained by cleaning ‘na’ values in survey data of MASS package to do the following:
```{r}
#install.packages("MASS")
library(MASS)
newSurvey = na.omit(survey)
```
1. Find the range of students’ age participated in the survey.
```{r}
age=newSurvey$Age
range(age)
```
2. Break the age range into non-overlapping sub-intervals by defining a sequence of equal distance break points of 10 by rounding the range to nearest integer.
```{r}
breaks = seq(16.917, 70.417, by=10)
breaks
```
3. Find the distribution of the age range according to the sub-intervals with cut with its right boundary opened. Display it in column form.
```{r}
age.cut = cut(age, breaks, right=FALSE)
age.freq = table(age.cut)
age.freq=cbind(age.freq) 
```
4. Which age range of students has mostly participated in the survey.
```{r}
age.freq[which.max(age.freq)]
```
5. Similarly, find the frequency distribution of Wr.Hnd span and display it in column format.
```{r}
wrHnd=newSurvey$Wr.Hnd
range(wrHnd)
```
```{r}
breaks = seq(13.0, 23.2, by=2)
breaks
```
```{r}
wrHnd.cut = cut(wrHnd, breaks, right=FALSE)
wrHnd.freq = table(wrHnd.cut)
wrHnd.freq=cbind(wrHnd.freq) 
wrHnd.freq
```
6. Find the relative frequency of Wr.Hnd and display it by correcting to 3 decimal places.
```{r}
wrHnd.relfreq = wrHnd.freq / nrow(newSurvey)
round(wrHnd.relfreq, 3)
```
