---
title: "CSE3505_FDA_Lab_Exp_1"
author: "20BCE1025_Abhishek_N_N"
date: "2022-08-16"
output: pdf_document
---
## Contents
1. Lab 1 Exercise Understanding Basic Data Types in R
2. Lab 1 Sample Practice

# Lab 1 Exercise Understanding Basic Data Types in R

```{r}
rm(list=ls())
```

1) initial decimal money let it be A
```{r}
A<-10.5
A
```
2) class name of A
```{r}
class(A)
```
3) checking A is numeric?
```{r}
is.numeric(A)
```
4) integer value to B and Displaying it
```{r}
B<-5
B
```
5) check B is Integer ?
```{r}
is.integer(B)
```

6) variable c to store rupee part of A
```{r}
C<-as.integer(A)
C
```
7) cost of one chocolate
```{r}
cost=C/B
cost
```
8) representing money as char string
```{r}
as.character(A)
```
9) storing first and last name of kid
```{r}
first_name<-"Jai"
last_name<-"Ganesh"
```
10) displaying message
```{r}
message<-paste(first_name,last_name,"bought" ,as.character(B) ,"chocolates")
message
```


11) extracting "Little" from "Twinkle Twinkle Little Star"
```{r}
rhymes<-"Twinkle Twinkle Little Star"
rhymes
```
```{r}
extracted_text=substr(rhymes, 17, 22)
extracted_text
```
12) replacing little as big
```{r}
library("stringr")
rhymes<-sub( "Little", "Big",rhymes)
rhymes
```
13) complex no to x
```{r}
x<-2+3i
x
```
14) real part of x
```{r}
Re(x)
```
15) imaginary part of x
```{r}
Im(x)
```
16) computing square root of negative number
```{r}
sqrt(as.complex(-15))
```

# Lab 1 Sample Practice
assign and print a variable
```{r}
x<-1
print(x)
```
```{r}
x
```
```{r}
msg="hello"
msg
```
```{r}
typeof(x)
```
```{r}
typeof(msg)
```
explicit and implicit printing
```{r}
x<-1:20
print(x)
x
```
```{r}
rollNo<-1:70
rollNo
```
```{r}
y<-20:30
y
```
```{r}
x<-c(0.5,0.6)
x
```
```{r}
x<-c(TRUE,FALSE)
x
```
```{r}
x<-c(T,F)
x
```
```{r}
x<-c("a","b","c")
x
```
```{r}
x=9:29
x
```
```{r}
x=c(1+0i,2+4i)
x
```
```{r}
x<-vector("numeric",length=10)
x
```
to get help
```{r}
?type
```
```{r}
help(type)
```

```{r}
y1<-c(1.7,"a")
y1
```
```{r}
y2=c(TRUE,2)
y2
```
```{r}
y3<-c("a",TRUE);y3
```
```{r}
class(y1)
class(y2)
class(y3)
```
```{r}
y11<-c(1.7,"3.2")
y11
class(y11)
```
```{r}
y22<-c(FALSE,TRUE)
y22
class(y22)
```

-------------------------
Explicit Coercion
-------------------------
```{r}
x<-0:6
x
class(x)
```
```{r}
y=as.numeric(x)
y
class(y)
```
```{r}
z=as.character(x)
z
class(z)
```
```{r}
l=as.logical(x)
l
class(l)
```
```{r}
com=as.complex(x)
com
class(com)
```