---
title: "Lab 1 Exercise Understanding Basic Data Types in R.nb"
output: html_notebook
---

```{r}
rm(list=ls())
```

1) initial decimal money let it be A
```{r}
A<-10.5
A
```
2) class name of A
```{r}
class(A)
```
3) checking A is numeric?
```{r}
is.numeric(A)
```
4) integer value to B and Displaying it
```{r}
B<-5
B
```
5) check B is Integer ?
```{r}
is.integer(B)
```

6) variable c to store rupee part of A
```{r}
C<-as.integer(A)
C
```
7) cost of one chocolate
```{r}
cost=C/B
cost
```
8) representing money as char string
```{r}
as.character(A)
```
9) storing first and last name of kid
```{r}
first_name<-"Jai"
last_name<-"Ganesh"
```
10) displaying message
```{r}
message<-paste(first_name,last_name,"bought" ,as.character(B) ,"chocolates")
message
```


11) extracting "Little" from "Twinkle Twinkle Little Star"
```{r}
rhymes<-"Twinkle Twinkle Little Star"
rhymes
```
```{r}
extracted_text=substr(rhymes, 17, 22)
extracted_text
```
12) replacing little as big
```{r}
library("stringr")
rhymes<-sub( "Little", "Big",rhymes)
rhymes
```
13) complex no to x
```{r}
x<-2+3i
x
```
14) real part of x
```{r}
Re(x)
```
15) imaginary part of x
```{r}
Im(x)
```
16) computing square root of negative number
```{r}
sqrt(as.complex(-15))
```

