---
title: "20BCE1025_Abhishek_N_N_Lab_6_Exp-6 Statistical Analysis of qualitative data"
author: "20BCE1025 Abhishek N N"
date: "20/09/2022"
output: pdf_document
---
Use the survey data in MASS package to do the following:

1. Import the package MASS
```{r}
library("MASS")
```
2. List the rows of data that has missing values.
```{r}
survey[rowSums(is.na(survey)) > 0,]
#or
survey[!complete.cases(survey),]
```
3. Create a data frame ‘newsurvey’ that contains the survey data after removing the na values. Use it for answering further queries
```{r}
newsurvey<-na.omit(survey)
```
4. How many male and female students participated in the survey?
```{r}
table(newsurvey["Sex"])
```
5. How many the left and right handers are there?
```{r}
table(newsurvey["W.Hnd"])
```
6. Find the relative frequency distribution of left and right handers and display them with the precision of two decimal places.
```{r}
round(table(newsurvey["W.Hnd"])/length(newsurvey$W.Hnd),2)
```
7. Display the male left hander and female left hander in the column format.
```{r}
t <- tapply(newsurvey$W.Hnd, newsurvey$Sex, table)
t<-unname(unlist(t))
d <-
  data.frame(
    male_left_hander = c(t[3]),
    female_left_hander = c(t[1])
  )
d
```
8. What percentage of male left handers never smokes?
```{r}
#install.packages("dplyr")
library("dplyr")
```

```{r}
male_left_never=length(filter(newsurvey, Sex=="Male" & W.Hnd=="Left" & Smoke=="Never"))
male_left=length(filter(newsurvey, Sex=="Male" & W.Hnd=="Left"))
male_left_never/male_left*100
```


































