---
title: "CSE3505_FDA_Lab_Exp_2"
author: "20BCE1025_Abhishek_N_N"
date: "2022-08-17"
output: pdf_document
---
# Working with Vectors in R

1. Create vector ‘class’ to store the class names ‘class1’,’class2’,…,’class5’ 
```{r}
class <- c("class1","class2","class3","class4","class5")
class
```

2. Use assign() function to create a vector ‘avg’ to store the average marks. 
```{r}
avg <- c(0,0,0,0,0)
assign("avg", c(80, 90, 95, 50, 70))
avg
```

3. Display the average mark of class2.
```{r}
avg[2]
```

4. Display all the average marks except class 2.
```{r}
avg[c(TRUE,FALSE,TRUE,TRUE,TRUE)]
```

5. Access the average mark of class4 by its name.
```{r}
avg[match("class4",class)]
```

6. Find the minimum average mark and print the class which scored it.
```{r}
min(avg)
class[which.min(avg)]
```

7. Find the maximum average mark and print the class which scored it.
```{r}
max(avg)
class[which.max(avg)]
```

8. Find the total of average marks scored by all classes.
```{r}
sum(avg)
```

9. Find the mean of the average marks scored by all classes.
```{r}
mean(avg)
```


10. Find the standard deviation of the average marks scored by all classes.
```{r}
sd(avg)
```

11. Arrange the average marks in ascending order.
```{r}
avg<-sort(avg)
avg
```

12. Create a vector classes by repeat the vector class twice.
```{r}
classes<-rep(class, times=2)
classes
```

13. Create a vector marks by repeating each average mark twice.
```{r}
marks<-rep(avg, times=2)
marks
```

14. Create a vector ‘report’ by adding the vector ‘avg’ with a sequence of 10 to 1 and find its length.
```{r}
report <- c(avg,10:1)
report
length(report)
```

15. Identify the classes for which average marks>70.
```{r}
for(a in avg){
  if (a>70) print(a)
}
```























